---
title: "Covid91 vaccine study Final2024"
author: "Put your name here!"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="finalSumr2024.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

$H_0$ The new preventative vaccine is independent on subpopluation
$H_A$ The new preventative vaccine is depenendent on subpopulation

Males- categorical
Females- categorical
LGBTQ- Categorical
Druggies- Categorical

They are all categorical so we will be using the cat~cat helper file.

## Males

## Method

Question: Is the covid19 vaccine effective in male?
$H_0$: The vaccine is not effective in preventing covid19 in males

$H_A$: The vaccine is effective in preventing covid19 in males

infected~sex(M)
categorical~categorical

We'll be using Cat~Cat


## Graphical results
```{r}
male <- FinalDat[FinalDat$sex=='M',]

```

```{r}
barchartGC(~infected + treatment,data=male)
barchartGC(~infected + treatment,data=male, type="percent")

```
##Numerical Results
```{r}
table1 <- xtabs(~infected+ treatment, data=male)
rowPerc(table1)
colPerc(table1)
```

## Inferential results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
 
 
##Conclusion


## Females

## Graphical Results
```{r}
Female <- FinalDat[FinalDat$sex=='F',]

```


```{r}
barchartGC(~infected + treatment,data=Female)
barchartGC(~infected + treatment,data=Female, type="percent")

```

##Numerical Results
```{r}
table1 <- xtabs(~infected+ treatment, data=Female)
rowPerc(table1)
colPerc(table1)
```

## Inferential results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


##Conclusions


## LGBTQ


##Grapical results

```{r}
barchartGC(~LGBTQ + treatment,data=FinalData)
barchartGC(~LGBTQ + treatment,data=FinalData, type="percent")

```
## Numerical results


```{r}
table1 <- xtabs(~LGBTQ + treatment, data=FinalData)
rowPerc(table1)
colPerc(table1)
```

## Inferential 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

##Conclusion


## Druggies

## Grapical results

```{r}
barchartGC(~DrugUser + treatment,data=FinalData)
barchartGC(~DrugUser + treatment,data=FinalData, type="percent")

```



## Numerical results

```{r}
table1 <- xtabs(~DrugUser + treatment, data=FinalData)
rowPerc(table1)
colPerc(table1)
```
## Inferential 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

##Conclusion



# Overall Results and Conclusions